%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Classicthesis-Styled CV
% LaTeX Template
% Version 1.0 (22/2/13)
%
% This template has been downloaded from:
% http://www.LaTeXTemplates.com
%
% Original author:
% Alessandro Plasmati
%
% License:
% CC BY-NC-SA 3.0 (http://creativecommons.org/licenses/by-nc-sa/3.0/)
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%----------------------------------------------------------------------------------------
%	PACKAGES AND OTHER DOCUMENT CONFIGURATIONS
%----------------------------------------------------------------------------------------

\documentclass{scrartcl}

\reversemarginpar % Move the margin to the left of the page 

\newcommand{\MarginText}[1]{\marginpar{\raggedleft\itshape\small#1}} % New command defining the margin text style

\usepackage[nochapters]{classicthesis} % Use the classicthesis style for the style of the document
\usepackage[LabelsAligned]{currvita} % Use the currvita style for the layout of the document

\renewcommand{\cvheadingfont}{\LARGE\color{Maroon}} % Font color of your name at the top

\usepackage{hyperref} % Required for adding links	and customizing them
\hypersetup{colorlinks, breaklinks, urlcolor=Maroon, linkcolor=Maroon} % Set link colors

\newlength{\datebox}\settowidth{\datebox}{2015-Present} % Set the width of the date box in each block

\newcommand{\NewEntry}[3]{\noindent\hangindent=2em\hangafter=0 \parbox{\datebox}{\small \textit{#1}}\hspace #2 #3 % Define a command for each new block - change spacing and font sizes here: #1 is the left margin, #2 is the italic date field and #3 is the position/employer/location field
\vspace{0.5em}} % Add some white space after each new entry

\newcommand{\Description}[1]{\hangindent=2em\hangafter=0\noindent\raggedright\footnotesize{#1}\par\normalsize\vspace{1em}} % Define a command for descriptions of each entry - change spacing and font sizes here

%----------------------------------------------------------------------------------------

\begin{document}

\thispagestyle{empty} % Stop the page count at the bottom of the first page

%----------------------------------------------------------------------------------------
%	NAME AND CONTACT INFORMATION SECTION
%----------------------------------------------------------------------------------------

\begin{cv}{\spacedallcaps{Stuart Nygard}}\vspace{1.5em} % Your name

\noindent\spacedlowsmallcaps{Personal Information}\vspace{0.5em} % Personal information heading

\NewEntry{}{\textit{Born}}{5 November 1989} % Birthplace and date

\NewEntry{email}{\href{mailto:stuart.a.nygard@gmail.com}{stuart.a.nygard@gmail.com}} % Email address

\NewEntry{phone}{(M) +1 (701) 571 6565}

\vspace{1em} % Extra white space between the personal information section and goal

\noindent\spacedlowsmallcaps{Goal}\vspace{1em} % Goal heading, could be used for a quotation or short profile instead


%----------------------------------------------------------------------------------------
%	EDUCATION
%----------------------------------------------------------------------------------------

\spacedlowsmallcaps{Education}\vspace{1em}

\NewEntry{2013-2015}{Boise State University}

\Description{\MarginText{Master of Science in Mathematics}GPA: 3.9\ \ $\cdotp$\ \ School: Arts and Sciences \newline
Thesis: \textit{The Density Topology on the Reals, with Analogues on Other Spaces}\ \ \newline
The thesis explored a refinement of the Euclidean topology on the reals, generated by sets which are 'almost' open in the sense of Lebesgue measure.\newline
Advisors: Dr. Zach \textsc{Teitler} and Dr. Andr\'es \textsc{Caicedo}}

%------------------------------------------------

\NewEntry{2008-2012}{The Catholic University of America}

\Description{\MarginText{Bachelor of Science in Mathematics}GPA: 3.77\ \ $\cdotp$\ \ \textit{Magna Cum Laude}\ \ $\cdotp$\ \textit{University Honors} $\cdotp$ \textit{Math Department Honors} \newline
Description: The degree was focused around a liberal arts core, with higher level math classes starting in the sophomore year.}

%------------------------------------------------

\NewEntry{Fall 2010}{Budapest Semesters in Mathematics}

\Description{\MarginText{Study Abroad in Mathematics}\textit{Courses in English}\ \ $\cdotp$\ \textit{Hungarian Language Study} $\cdotp$ \textit{Travel} \newline
Description: This program is taught by members of the renowned R\'enyi Institute. The program is geared toward high-achieving math undergraduates.}

%------------------------------------------------

\vspace{1em} % Extra space between major sections

%----------------------------------------------------------------------------------------
%	WORK EXPERIENCE
%----------------------------------------------------------------------------------------

\noindent\spacedlowsmallcaps{Work Experience}\vspace{1em}

\NewEntry{2015--Present}{Device Characterization Engineer, \textsc{Micron}}

\Description{\MarginText{Micron Technology}
Researched novel memory chip solutions. Characterized electrical properties of cells to determine results of process experiments. Implemented custom scripts for data analysis, reporting, testing, etc. Create new metrics for device quality. Develop cross-team strategy for software, testing, and data analytics.}

%------------------------------------------------

\NewEntry{2015}{Device Characterization Intern, \textsc{Micron}}

\Description{\MarginText{Micron Technology}Wrote software to automate characterization and testing processes. Worked closely with engineers to facilitate faster, more flexible tests.}

%------------------------------------------------

\NewEntry{2014-2016}{Graduate Assistant / Adjunct Prof., \textsc{Boise State}}

\Description{\MarginText{Boise State University}Developed lesson plans and tests based on departmental curriculum. Taught classes in algebra, precalculus, and trigonometry. Also served as after-hours tutor in departmental help center.}

%------------------------------------------------

\NewEntry{2013-2014}{Wireline Operator, \textsc{Penkota Wireline}}

\Description{\MarginText{Penkota Wireline}Drove commercial trucks. Moved and operated wireline equipment for performing remote operations on oil drilling rigs. Handled welding, fabrication, and explosives in shop and in the field.}

%------------------------------------------------

\newpage % Extra space between major sections

%----------------------------------------------------------------------------------------
%	PUBLICATIONS
%----------------------------------------------------------------------------------------

\spacedlowsmallcaps{Presentations}\vspace{1em}

\NewEntry{4 March 2016}{\small{The Density Topology with Analogues on Other Spaces}}

\Description{\MarginText{Boise State University}
The density topology is a topology based on sets which are 'almost open' in the Euclidean topology. Starting from Lebesgue measure, the thesis demonstrates the density topology as a refinement of the Euclidean topology, and explores separation and connectedness properties of the density topology.\\ Advisors: Drs. Zach \textsc{Teitler} and Andr\'es \textsc{Caicedo}}

%------------------------------------------------

\NewEntry{25 Jan. 2015}{\small{A Survey of the Density Topology}}

\Description{\MarginText{The Winter School\\in Set Theory}
This presentation was an expository talk given during the preliminary research into the master's thesis. The presentation discussed the definitions and basic properties of the topology without attempting to demonstrate analogues on other spaces.\\ Organizer: Dr. Jonathan \textsc{Verner}}

%------------------------------------------------

\NewEntry{5 May 2014}{\small{A Feistel-Like Network Using Pr\"ufer Coding of Trees}}

\Description{\MarginText{BoiseCrypt Conference}Consider a plaintext message to be a sequence of elements. Using Pr\"ufer's algorithm, the sequence can be mapped into the space of enumerated trees, in the sense of graph theory. The trees can be manipulated in this space with chaotic results in the sequence space.\\ Organizer: Dr. Liljana \textsc{Babinkostova}}

%------------------------------------------------

\vspace{1em} % Extra space between major sections

%----------------------------------------------------------------------------------------
%	COMPUTER SKILLS
%----------------------------------------------------------------------------------------

\spacedlowsmallcaps{Computer Skills}\vspace{1em}

\Description{\MarginText{Basic}Javascript, Elm, SQL}

\Description{\MarginText{Intermediate}Perl, Redis, Docker, Jupyter, }

\Description{\MarginText{Advanced}Python, HTML, \LaTex, Linux, Windows}

%------------------------------------------------

\vspace{1em} % Extra space between major sections

%----------------------------------------------------------------------------------------
%	OTHER INFORMATION
%----------------------------------------------------------------------------------------

\spacedlowsmallcaps{Other Information}\vspace{1em}

\newlength{\langbox} % Create a new length for the length of languages to keep them equally spaced
\settowidth{\langbox}{Hungarian} % Length equals the length of "English" - if you have a longer language in your list put it here

\Description{\MarginText{Languages}\parbox{\langbox}{\textsc{English}}\ \ $\cdotp$\ \ \ Mothertongue}

\vspace{-0.5em} % Negative vertical space to counteract the vertical space between every \Description command

\Description{\parbox{\langbox}{\textsc{German}}\ \ $\cdotp$\ \ \ Intermediate (conversational)}

\vspace{-0.5em} % Negative vertical space to counteract the vertical space between every \Description command

\Description{\parbox{\langbox}{\textsc{Hungarian}}\ \ $\cdotp$\ \ \ Beginner}

\vspace{1em} % Negative vertical space to counteract the vertical space between every \Description command

%------------------------------------------------

\Description{\MarginText{Interests}Banjo\ \ $\cdotp$\ \ Ultimate Frisbee\ \ $\cdotp$\ \ Running\ \ $\cdotp$\ \ Languages\ \ $\cdotp$\ \ Calligraphy}

%----------------------------------------------------------------------------------------

\end{cv}

\end{document}
